On modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2019-03-28 docs/mvfits_paper/mvf.tex
Reword symbol space and lambda_bulk defs [5,6]
Add note for kappa mapping orientation change [7]

Each term is an element of the tensor-product of the power-sets of each model dimension. That is $\mlam_{bulk} = \{x_0,x_1 .. x_N, ... x_0^1, x_0^2, x_0^3, ...  , (x_0^K x_1^K ... x_N^K) \}$.

@@

appropriately linearizes the sharp behavior of each frequency near $\jf=1$ while also mapping $-1 \le \jf \le 1$ onto $0 \le \kappa \le 1$.

>>>>

Each term is an element of the tensor-product of the sets of powers of each coordinate of a chosen representation of the models domain. That is $\mlam_{bulk} = \{x_0^{d_0} x_1^{d_1} \ldots x_N^{d_N} \mid d_i \in \{0,\ldots,K\}, i \in \{0,\ldots,N\}\}$.

@@

appropriately linearizes the sharp behavior of each frequency near $\jf=1$ while also mapping $-1 \le \jf \le 1$ onto $0 \le \kappa \le 1$. Note that under the mapping $j_f \mapsto \kappa$ the orientation is reversed such that as $j_f \rightarrow 1$ from below $\kappa \rightarrow 0$ from above.
